Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-09 ms.tex
colors

  > 0.02$ are denoted as {\bf TI}.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{mdot_sfr.pdf}
\caption{\label{fig:bh_growth} {\it Top panel:} Critical values of the
  black hole accretion rate $\dot{M}$ in Eddington units as a function
  of black hole mass $M_{\bullet}$, shown separately for core
  ($\Gamma=0.1$, solid lines) and cusp galaxies ($\Gamma=0.8$,
  dot-dashed lines).  Black lines show the accretion rate calculated
  from equation (\ref{eq:eddr_analytic}) using our estimate of the gas
  heating rate provided at $z = 0$ by the average star formation
  histories for each galaxy mass (Fig.~\ref{fig:vwSources}).  Green
  lines show the maximum accretion set by Ia supernovae blow-out
  (\ref{eq:eddr_Ia}).  Red lines show the accretion rate so obtained
  if Compton heating alone was acting (eq.~[\ref{eq:MdotC}]).  Yellow
  lines show the maximum accretion rate for a thermally stable flow
  near the stagnation radius (eq.~[\ref{eq:Mdotmax}]).  We also show
  Eddington ratios inferred for SgrA* from
  \citet{Quataert:2004a} (black circles), for NGC3115 from
  \citet{ShcherbakovWong+:2014a} (black diamonds), and for
  the Swift J1644+57 TDE from \citet{BergerZauderer+:2012a} (black crosses) {\it Bottom panel:} Growth times $\Mbh/\Mdot$
  in units of the Hubble time $\th$ for each of the accretion rates
  shown in the top panel.}
\end{figure}

>>>>

  \geq 0.02$ are denoted as {\bf TI}.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{mdot_sfr.pdf}
\caption{\label{fig:bh_growth} {\it Top panel:} Critical values of the
  black hole accretion rate $\dot{M}$ in Eddington units as a function
  of black hole mass $M_{\bullet}$, shown separately for core
  ($\Gamma=0.1$, solid lines) and cusp galaxies ($\Gamma=0.8$,
  dot-dashed lines).  Black lines show the accretion rate calculated
  from equation (\ref{eq:eddr_analytic}) using our estimate of the gas
  heating rate provided at $z = 0$ by the average star formation
  histories for each galaxy mass (Fig.~\ref{fig:vwSources}).  Teal
  lines show the maximum accretion set by Ia supernovae blow-out
  (\ref{eq:eddr_Ia}).  Red lines show the accretion rate so obtained
  if Compton heating alone was acting (eq.~[\ref{eq:MdotC}]).  Yellow
  lines show the maximum accretion rate for a thermally stable flow
  near the stagnation radius (eq.~[\ref{eq:Mdotmax}]).  We also show
  Eddington ratios inferred for SgrA* from \citet{Quataert:2004a}
  (gray circles), for NGC3115 from \citet{ShcherbakovWong+:2014a}
  (gray diamonds), and for the Swift J1644+57 TDE from
  \citet{BergerZauderer+:2012a} (gray triangles) {\it Bottom panel:}
  Growth times $\Mbh/\Mdot$ in units of the Hubble time $\th$ for each
  of the accretion rates shown in the top panel.}
\end{figure}
